Title Goes Here

### 2020-03-09 analysis/paper/paper.Rmd
Putting methods

---
title: "Title Goes Here"
author:
  - Yichun Chen:
      email: fl@oneplace.edu
      institute: [UofO]
      correspondence: true
  - Ben Marwick:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

# Methods

# Results

@@

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

>>>>

---
title: "Title Goes Here"
author:
  - Yichun Chen:
      email: yichun33@uw.edu
      institute: [UofO]
      correspondence: true
  - Ben Marwick:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

# Methods
We collected lists of the people that presented research at recent SAA (2016 with 905 presenters, 2017 with 992 presenters, 2018 with 3512 presenters, 2019 with 1014 presenters) EAA (2018 with 2928 presenters) and CAA (2018 with 358 presenters) conferences. We obtained publically available programs of these conferences and also tidied the data into a rectangular form with variables including the primary author’s first name, last name and the title of their presentation. We used R and the gender package (Mullen 2018; Mihaljević 2019; Belvis et al. 2015) to predict the gender of all first-named presenters in our sample. We used the gender package to identify a first name as male or female, based on a probability scale computed from government records of name-gender data, specifically US Social Security Administration (SSA) baby name data [citation]. This method has the advantage of speed and ease of automation, but also some substantial limitations. We are only able to infer gender into binary male/female genders and assign probabilities for the first names into these categories. This has the unfortunate result of excluding other genders from the results, and we encourage conference organisers to collect gender data directly from participants to improve the representation of minority genders in future studies. The package often fails to classify non-English names, as the SSA data the package uses are mostly in English names. This means that people with non-English names are underrepresented in our results. To remove names where gender is ambiguous, which we define as a similar proportion of males and females having that name in the SSA data, we excluded names where the difference in proportions was less than 0.47, a figure we obtained by exploratory data analysis. It is important to note that the gender designations here are not self-identified by the presenters, but are computed probabilistically. Better quality data will come if presenters self-identify their gender, but we have no alternative because currently these data are not available. Our hope is that this work, despite its many limitations, will stimulate the collection of more reliable, justifiable, and useful data by conference organisers. 
# Results

@@

The current Git commit details are:
u
```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
